---
title: "GitHub Workflow"
output: html_document
date: "2024-06-04"
---

## Steps for linking GitHub to Posit Cloud 

```{r}
install.packages("usethis")
library("usethis")
```


```{r}

usethis::create_github_token()
gitcreds::gitcreds_set()
use_git_config(user.name = "cansavvy", user.email = "cansav09@gmail.com")
```


```{r}
git_sitrep()
```


## Rundown on GitHub vocab 

Repository = house for your project files
Cloning = Making a copy of the repository for posit cloud (or wherever you are working)
Personal Access Token = A key or fancy password to give us access to GitHub 
Commit = Adding some file changes to a branch 
Pushing = A transfer of files from where we are working to GitHub 


## Creating a pull request

Create a new branch to work from. (that's different than the default main branch). 

```{r}
pr_init(branch = "new-branch")
```

Make a file change (and save it). 

In the Git tab, check the "staged" box next to the file change you made. 

Click the commit button. 
Write a descriptive commit message. 
Click "commit". Now we can close this window. 

```{r}
pr_push()
```

This will open up a window in Github that creates a pull request. 

Pull Request = Its a method to suggest changes to the files
